### 2022-10-26 manuscript.tex
Updating citations [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/891e1faad1b05462ff855da04e5af9c7a676855d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/891e1faad1b05462ff855da04e5af9c7a676855d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332227852

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/e15161667619fdac1d5235514e3585de24f91b37/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/e15161667619fdac1d5235514e3585de24f91b37}{SORTEE-Github-Hackathon/manuscript@e151616}
on October 26, 2022.

@@

Conventional research practices typically separate tasks among collaborators (\emph{i.e.}, data entry, analysis, writing).
It is common that coauthors discuss, but do not actively verify, edit, or execute research tasks that are not their main responsibility.
GitHub can serve as a tool for open and tractable research development.
Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, (\protect\hyperlink{ref-18PTmKJkq}{January 18 \& Pm, 2020})).
Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.

@@

GitHub can facilitate project continuity among research code by making code handover easier (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}; \protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
Repositories and organizations can have designated data and code owners (or more appropriate, stewards; see (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}), (\protect\hyperlink{ref-s91uGRZ2}{\emph{About Code Owners}, n.d.})), who can also can change through time allowing for the transition of code between research cohorts.
Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.

@@

Automation has a strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.}, (\protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018})), automated data analysis (\emph{e.g.}, (\protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017})), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, (\protect\hyperlink{ref-SirQKFIz}{White et al., 2018})).
In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see (\protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015})).
In addition to increasing scientific rigor and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (\protect\hyperlink{ref-mmCOSRfr}{McIntire et al., 2022}), long-term ecological studies (\protect\hyperlink{ref-RxK4CmfR}{Ernest et al., 2018}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), and management of species at risk information (\protect\hyperlink{ref-kZzfmBNu}{Naujokaitis-Lewis et al., 2022}).

Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI(\protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}), Travis CI(\protect\hyperlink{ref-YeFSbfFV}{\emph{Homepage \textbar{} Travis CI -- Start Building Today!}, n.d.})).
Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
These actions are highly configurable and have numerous applications, such as automatically running analyses and creating figures when data or code are updated, incorporating changes to websites or applications, testing modifications to software (\emph{e.g.}, R or Python libraries).
Action workflows can be found in GitHub's Marketplace (\url{https://github.com/marketplace?type=actions}) or, alternatively, in open user repositories.

@@

\leavevmode\vadjust pre{\hypertarget{ref-18PTmKJkq}{}}%
January 18, P. L. B. K., \& Pm, 2022. 2:51. (2020, February 4). \#PruittData and the Ethics of Data in Science. \emph{Ecology for the Masses}. \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science/}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/891e1faad1b05462ff855da04e5af9c7a676855d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/891e1faad1b05462ff855da04e5af9c7a676855d}{SORTEE-Github-Hackathon/manuscript@891e1fa}
on October 26, 2022.

@@

Conventional research practices typically separate tasks among collaborators (\emph{i.e.}, data entry, analysis, writing).
It is common that coauthors discuss, but do not actively verify, edit, or execute research tasks that are not their main responsibility.
GitHub can serve as a tool for open and tractable research development.
Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science}).
Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.

@@

GitHub can facilitate project continuity among research code by making code handover easier (\protect\hyperlink{ref-D4C4k4ak}{Fehr et al., 2021}; \protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
Through version control, the history of code and data from projects in ecology and evolution can be tracked accessible to future laboratory members and collaborators (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}).
Repositories and organizations can have designated data and code owners {[}or more appropriate, stewards; see Hampton et al. (\protect\hyperlink{ref-iIEKCTLU}{2015}), \emph{About Code Owners} (\protect\hyperlink{ref-s91uGRZ2}{n.d.}){]}, who can also can change through time allowing for the transition of code between research cohorts.
Other project collaborators can contribute to repository design and development, and their active involvement can both aid authors ability to act as guarantors of the project, and the clarity and reproducibility of the project for future users.
In (Figure \ref{fig:github-diagram}), we highlight several elements of good repository structure, and the various ways that contributors may interact with them.

@@

Automation has a strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
Automation frameworks can streamline many stages of the scientific process, including automated data collection and data validation (\emph{e.g.}, \protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-lXvpQxeN}{Yenni et al., 2018}), automated data analysis (\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017}), automated archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{White et al., 2018}).
In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see \protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015}).
In addition to increasing scientific rigor and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (\protect\hyperlink{ref-mmCOSRfr}{McIntire et al., 2022}), long-term ecological studies (\protect\hyperlink{ref-RxK4CmfR}{Ernest et al., 2018}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), and management of species at risk information (\protect\hyperlink{ref-kZzfmBNu}{Naujokaitis-Lewis et al., 2022}).

Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI, \protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}); Travis CI, \emph{Homepage \textbar{} Travis CI -- Start Building Today!} (\protect\hyperlink{ref-YeFSbfFV}{n.d.}){]}.
Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
These actions are highly configurable and have numerous applications, such as automatically running analyses and creating figures when data or code are updated, incorporating changes to websites or applications, testing modifications to software (\emph{e.g.}, R or Python libraries).
Action workflows can be found in GitHub's Marketplace (\url{https://github.com/marketplace?type=actions}) or, alternatively, in open user repositories.

@@
